```{r}
#Consider the following customer: Age=40, Experience=10, Income=84, Family=2, CCAvg=2, Education2=1, Education3=0, Mortgage=O, Securities Account=O, CD Account=O, Online=1 and Credit.card = 1. Perform a k-NN classification with all predictors except ID and ZIP code using k = 1. Remember to transform categorical predictors with more than two categories into dummy variables first. Specify the success class as 1 (loan acceptance), and use the default cutoff value of 0.5. How would this customer be classified?

library(readxl)
library(caret)
library(lattice)
library(class)
UB<-read_excel("UniversalBank.xlsx",sheet="Data")
#According to the question, we need to add two columns education2 and education 3 also we need to make the education2=1, education3=0 
UB$Education1<-- (ifelse(UB[,8]==1,1,0))
UB$Education2 <- (ifelse(UB[,8]==2,1,0))
UB$Education3 <- (ifelse(UB[,8]==3,1,0))
#According to the requirment the first step is to partition the data into trainning data and Validation data 
trainingUB<- sample(row.names(UB), 0.6*dim(UB)[1])
ValidationUB<- setdiff(row.names(UB), trainingUB)
training.df <- UB[trainingUB,]
validation.df <- UB[ValidationUB,]

#View(UB)
#we also need to remove the columns we do not need 

training.new.df <- training.df[,-which(names(training.df) %in% c("ID","ZIP Code","Education"))]
validation.new.df <- validation.df[,-which(names(validation.df) %in% c("ID","ZIP Code","Education"))]

TS.df <- data.frame('Age'=40, 'Experience'=10, 'Income'=84, 'Family'=2, 
                           'CCAvg'=2,'Mortgage'=0, 'Education1'=0, 'Education2'=1, 
                           'Education3'=0,'Securities.Account'=0, 'CD.Account'=0,
                           'Online'=1,'CreditCard'= 1)

TS.norm <- TS.df
norm <- preProcess(training.new.df[,c(-7:-13)],method = c("center", "scale"))
TS.norm[,c(1:6)] <- predict(norm, TS.norm[,c(1:6)])
TS.norm
UB$`Personal Loan`<-factor(UB$`Personal Loan`)
Knn.test<-knn(train=training.new.df[,-7],test=TS.norm,cl=training.new.df$`Personal Loan`,k=1)
Knn.test

```
So, for the given data, we have a 0.

#Finding a value for k that balances between overfitting and ignoring the predictor information
```{r}
library(caret)
library(class)
library(lattice)
library(readxl)

UB<-read_excel("UniversalBank.xlsx",sheet="Data")
trainingUB<- sample(row.names(UB), 0.6*dim(UB)[1])
ValidationUB<- setdiff(row.names(UB), trainingUB)
training.df <- UB[trainingUB,]
validation.df <- UB[ValidationUB,]
training.new.df <- training.df[,-which(names(training.df) %in% c("ID","ZIP Code","Education"))]
validation.new.df <- validation.df[,-which(names(validation.df) %in% c("ID","ZIP Code","Education"))]
set.seed(5)
accuracy.a <- data.frame(k=seq(1,10,1),accuracy=rep(0,10))
for(i in c(1:10)){
   knn.pred<-knn(training.new.df[,-7],validation.new.df[,-7],
                 cl=training.new.df$`Personal Loan`,k = i)
                 accuracy.a[i,2]<-confusionMatrix(knn.pred,factor(validation.new.df$`Personal Loan`))$overall[1]
}

accuracy.a
plot(accuracy.a, type = "b")


 
``` 
Classification matrix for the validation data that results from using the best k.

k = 3
```{r}
pred_knn<-knn(training.new.df[,-7],validation.new.df[,-7],
                 cl=training.new.df$`Personal Loan`,k = 3)
pred_knn
confusionMatrix(pred_knn,factor(validation.new.df$`Personal Loan`))
```
Consider the following customer: Age=40, Experience=10, Income=84, Family=2, CCAvg=2, Education 1=0, Education 2=1, Education 3=0, Mortgage=0, Securities Account=0, CD Account=0, Online=1 and Credit Card=1. Classify the customer using the best k.

k = 3
```{r}
knn_test<-knn(train=training.new.df[,-7],test = validation.new.df[,-7],cl=training.new.df$`Personal Loan`, k=3)
knn_test
```
# Repartition the data, this time into training, validation, and test sets (50% : 30% : 20%). Apply the k-NN method with the k chosen above. Compare the classification matrix of the test set with that of the training and validation sets. Comment on the differences and their reason
#  Subset the data into traing,validation and test sets
```{r}
index_train <- sample(row.names(UB), 0.5*dim(UB)[1])
index_valid<- sample(row.names(UB), 0.3*dim(UB)[1])
index_test<- sample(row.names(UB), 0.2*dim(UB)[1])
df_train <- UB[index_train,]
df_valid<- UB[index_valid,]
df_test<- UB[index_test,]
```
# Remove variables 
```{r}
train_e<-df_train[,-which(names(df_train) %in% c("ID","ZIP Code","Education"))]
valid_e<-df_valid[,-which(names(df_valid) %in% c("ID","ZIP Code","Education"))]
test_e<-df_test[,-which(names(df_test) %in% c("ID","ZIP Code","Education"))]
```
# data normalization
```{r}
train_E<-train_e
valid_E<-valid_e
test_E<-test_e
train_E[1:6]<-as.data.frame(lapply(train_e[1:6],normalize))
valid_E[1:6]<-as.data.frame(lapply(valid_e[1:6],normalize))
test_E[1:6] <- as.data.frame(lapply(test_e[1:6],normalize))
```
# knn model
```{r}
knn_train <- knn(train_E[,-7],train_E[,-7],cl=train_E$`Personal Loan`,k = 3) 
knn_valid <- knn(train_E[,-7],valid_E[,-7],cl=train_E$`Personal Loan`,k = 3) 
knn_test <- knn(train_E[,-7],test_E[,-7],cl=train_E$`Personal Loan`,k = 3) 
head(knn_train)
head(knn_valid)
head(knn_test)

acc_e <- data.frame(subset=c('Train','Valid','Test'),accuracy=rep(0,3))
acc_e[1,2] <- confusionMatrix(knn_train,factor(train_E$`Personal Loan`))$overall[1]
acc_e[2,2] <- confusionMatrix(knn_valid,factor(train_E$`Personal Loan`))$overall[1]
acc_e[3,2] <- confusionMatrix(knn_test,factor(train_E$`Personal Loan`))$overall[1]
acc_e
```

When k=3, accuracy is equal to 0.903 






