```{r}
library(readxl)
Acc <- read_excel("Accidents.xlsx", sheet = "Data")

Acc$Injury <- as.factor(ifelse(Acc$MAX_SEV_IR < 1, "NO", "YES"))
Acc1 <- Acc[,-24]

index <- sample(1:nrow(Acc), size=0.5*nrow(Acc))
test <- Acc[index,]
train<- Acc[-index,]

library(e1071)
levels(train$Injury)
model1 <- naiveBayes(Injury~., data = train)
class(model1) 
p <- predict(model1,test)
table(p)

library(e1071)
Acc2 <-Acc1[1:12,c("Injury", "WEATHER_R", "TRAF_CON_R")]
Acc2
table(Acc2$WEATHER_R, Acc2$TRAF_CON_R, Acc2$Injury)

Acc2$Injury <- ifelse(Acc2$Injury == "YES", 1, 0)
Acc2$Injury <- as.factor(Acc2$Injury)

model2 <- naiveBayes(Injury ~ WEATHER_R + TRAF_CON_R, data = Acc2)
class(model2)

model3 <- predict(model2, Acc2)
table(model3)

Acc1$Injury<-ifelse(Acc1$Injury == "YES", 1, 0)
Acc1$Injury<-as.factor(Acc1$Injury)
train1<-Acc1[1:25310, ]
valid1<-Acc1[25311:42183, ]

model4 <- naiveBayes(Injury ~ HOUR_I_R + ALCHL_I + WKDY_I_R + LGTCON_I_R + MANCOL_I_R + SPD_LIM + VEH_INVL, data=train1)
model4

p2 <- predict(model4, valid1)
table(p2, valid1$Injury)
```
Probability of Yes is 50.87, and that of No is 49.12.


```{r}
Ac.df <- read_excel("Accidents.xlsx", sheet = "Data")
Ac.df$INJURY <- ifelse(Ac.df$MAX_SEV_IR>0, "Yes", "No")
Ac.df
x.df <- Ac.df[1:12,c("INJURY","WEATHER_R","TRAF_CON_R")]
x.df
```

```
ii) Exact Bayes calculation for INJURY=Yes

```{r}
#P(Injury=yes|WEATHER_R = 1, TRAF_CON_R =0):
n1 <- 2/3 * 3/12
d1 <- 3/12
prob1 <- n1/d1

#P(Injury=yes|WEATHER_R = 1, TRAF_CON_R =1):
n2 <- 0 * 3/12
d2 <- 1/12
prob2 <- n2/d2

#P(Injury=yes| WEATHER_R = 1, TRAF_CON_R =2):
n3 <- 0 * 3/12
d3 <- 1/12
prob3 <- n3/d3

#P(Injury=yes| WEATHER_R = 2, TRAF_CON_R =0):
n4 <- 1/3 * 3/12
d4 <- 6/12
prob4 <- n4/d4

#P(Injury=yes| WEATHER_R = 2, TRAF_CON_R =1):
n5 <- 0 * 3/12
d5 <- 1/12
prob5 <- n5/d5

#P(Injury=yes| WEATHER_R = 2, TRAF_CON_R =2):
n6 <- 0 * 3/12
d6 <- 0
prob6 <- n6/d6

x<-c(1,2,3,4,5,6)
y<-c(prob1,prob2,prob3,prob4,prob5,prob6)
prob.df<-data.frame(x,y)
names(prob.df)<-c('#','Probability')
prob.df
```


Classification of accidents with cutoff=0.5:
```{r}
acc1.prob<-x.df
head(acc1.prob)

prob.injury <- c(0.667, 0.167, 0, 0, 0.667, 0.167, 0.167, 0.667, 0.167, 0.167, 0.167, 0)
#acc1.prob['PROB_INJURY'] <- NA
acc1.prob$PROB_INJURY<-prob.injury


acc1.prob$PREDICT_PROB<-ifelse(acc1.prob$PROB_INJURY>0.5,"Yes","No")
acc1.prob
```
P(Injury = YES | WEATHER_R = 1, TRAF_CON_R = 0) = Yes
P(Injury = YES | WEATHER_R = 1, TRAF_CON_R = 1) = No
P(Injury = YES | WEATHER_R = 1, TRAF_CON_R = 2) = No
P(Injury = YES | WEATHER_R = 2, TRAF_CON_R = 0) = No
P(Injury = YES | WEATHER_R = 2, TRAF_CON_R = 1) = No
P(Injury = YES | WEATHER_R = 2, TRAF_CON_R = 2) = No
P(Injury = NO | WEATHER_R = 1, TRAF_CON_R = 0) = Yes
P(Injury = NO | WEATHER_R = 1, TRAF_CON_R = 1) = No
P(Injury = NO | WEATHER_R = 1, TRAF_CON_R = 2) = No
P(Injury = NO | WEATHER_R = 2, TRAF_CON_R = 0) = Yes
P(Injury = NO | WEATHER_R = 2, TRAF_CON_R = 1) = No
P(Injury = NO | WEATHER_R = 2, TRAF_CON_R = 2) = No

Naive Bayes:

```{r}
prob <- 2/3 * 0/3 * 3/12
prob
```
p(Injury=Yes|TRAF_CON_R=1, WEATHER_R=1)=0


```{r}
library(e1071)
library(klaR)
library(caret)
n1<-naiveBayes(INJURY ~ ., data = x.df)
predict(n1, newdata = x.df,type = "raw")

library(caret)
o1=x.df[,-3]
o2=x.df$INJURY
cla1 <- train(o1,o2,'nb', trControl = trainControl(method = 'cv',number=10))
cla1
pred<-predict(cla1$finalModel,o1)
pred
table(pred$class,o2)

```

From the following model, HOUR_I_R, ALCOHOL_I, WKDY_I_R, LGTCON_I_R,
MAN_COL_I, SPD_LIM can be included when weather conditions and location is not known.

Overall Error = (911+7275)/(7054+7275+911+1633)*100=48.51

There is no improvement in the model.

We get a probability of zero for the given conditional probability as Naive Bayes takes the probability of the category of predictor as zero.
