---
title: "Group 15 Homework 6"
authors: "Tushar Rao, Yiwei Li"
output: pdf_document
---

Problem 1
```{r}
library(readxl)
cars<- read_excel("18 Toyota Corolla.xlsx")
cars <- cars[c(3,4,7,9,12,13,19)]
```


Normalization
```{r}
normalize <- function(x) {
return ((x - min(x)) / (max(x) - min(x)))
}
cars <- as.data.frame(lapply(cars, normalize))
```

Splitting Dataset
```{r}
training=sample(row.names(cars), dim(cars)[1]*0.75)
validation=setdiff(row.names(cars), training)
trainData <- cars[training,c(1,2,3,4,6)]
validData <- cars[validation,c(1,2,3,4,6)]
```

Threshold=1
```{r}
library(neuralnet)
nn1 <- neuralnet(Price~Age_08_04+KM+HP+cc,data=trainData, linear.output=FALSE,threshold=1, algorithm ='rprop+')
training.prediction1 <- compute(nn1, trainData[,-1])
trainpred1<- training.prediction1$net.result
rmsetrain1 <- sqrt(mean((trainpred1-trainData$Price)^2))
validation.prediction1 <- compute(nn1, validData[,-1])
validpred1<- validation.prediction1$net.result
rmsevalid1 <- sqrt(mean((validpred1-validData$Price)^2))

```

Threshold=0.1
```{r}
nn2 <- neuralnet(Price~Age_08_04+KM+HP+cc,data=trainData, linear.output=FALSE,threshold=0.1,algorithm='rprop+')
training.prediction2 <- compute(nn2, trainData[,-1])
trainpred2<- training.prediction2$net.result
rmsetrain2 <- sqrt(mean((trainpred2-trainData$Price)^2))
validation.prediction2 <- compute(nn2, validData[,-1])
validpred2<- validation.prediction2$net.result
rmsevalid2 <- sqrt(mean((validpred2-validData$Price)^2))
```

Threshold=0.05
```{r}
nn3 <- neuralnet(Price~Age_08_04+KM+HP+cc,data=trainData, linear.output=FALSE,threshold=0.05, algorithm = 'rprop+')
training.prediction3 <- compute(nn3, trainData[,-1])
trainpred3<- training.prediction3$net.result
rmsetrain3 <- sqrt(mean((trainpred3-trainData$Price)^2))
validation.prediction3 <- compute(nn3, validData[,-1])
validpred3<- validation.prediction3$net.result
rmsevalid3 <- sqrt(mean((validpred3-validData$Price)^2))
```

Threshold=0.01
```{r}
nn4 <- neuralnet(Price~Age_08_04+KM+HP+cc,data=trainData, linear.output=FALSE,threshold=0.01, algorithm = 'rprop+')
training.prediction4 <- compute(nn4, trainData[,-1])
trainpred4<- training.prediction4$net.result
rmsetrain4 <- sqrt(mean((trainpred4-trainData$Price)^2))
validation.prediction4 <- compute(nn4, validData[,-1])
validpred4<- validation.prediction4$net.result
rmsevalid4 <- sqrt(mean((validpred4-validData$Price)^2))
```

Threshold = 0.005
```{r}
nn5 <- neuralnet(Price~Age_08_04+KM+HP+cc,data=trainData,linear.output=FALSE,threshold=0.005, algorithm = 'rprop+')
training.prediction5 <- compute(nn5, trainData[,-1])
trainpred5<- training.prediction5$net.result
rmsetrain5 <- sqrt(mean((trainpred5-trainData$Price)^2))
validation.prediction5 <- compute(nn5, validData[,-1])
validpred5<- validation.prediction5$net.result
rmsevalid5 <- sqrt(mean((validpred5-validData$Price)^2))
```

Threshold = 0.001
```{r}
nn6 <- neuralnet(Price~Age_08_04+KM+HP+cc,data=trainData, linear.output=FALSE,threshold=0.001, algorithm = 'rprop+')
training.prediction6 <- compute(nn6, trainData[,-1])
trainpred6<- training.prediction6$net.result
rmsetrain6 <- sqrt(mean((trainpred6-trainData$Price)^2))
validation.prediction6 <- compute(nn6, validData[,-1])
validpred6<- validation.prediction6$net.result
rmsevalid6 <- sqrt(mean((validpred6-validData$Price)^2))
```

Threshold = 0.0001
```{r}
nn7 <- neuralnet(Price~Age_08_04+KM+HP+cc,data=trainData, linear.output=FALSE,threshold=0.0001, algorithm = 'rprop+')
training.prediction7 <- compute(nn7, trainData[,-1])
trainpred7<- training.prediction7$net.result
rmsetrain7<- sqrt(mean((trainpred7-trainData$Price)^2))
validation.prediction7 <- compute(nn7, validData[,-1])
validpred7<- validation.prediction7$net.result
rmsevalid7<- sqrt(mean((validpred7-validData$Price)^2))
```

RMSE Values for all the neural nets for training data and test data

```{r}
rmsetrain<-rbind(rmsetrain1, rmsetrain2,rmsetrain3, rmsetrain4,rmsetrain5, rmsetrain6,rmsetrain7)
rmsevalid<-rbind(rmsevalid1, rmsevalid2,rmsevalid3, rmsevalid4,rmsevalid5, rmsevalid6,rmsevalid7)
rmsetrain
rmsevalid
```
a)With decrese in threshold, RMS error also decreases for training data.

b)With decrese in threshold, RMS error also decreases for training data.

c) Neural nets with different number of nodes(n) in hidden layer

All the neural networks until now had the number of hidden layer nodes as 1 by default.

n=2
```{r}
nn8 <- neuralnet(Price~Age_08_04+KM+HP+cc, data=trainData,
linear.output=FALSE,threshold=1, algorithm = 'rprop+',hidden=2)
training.prediction8 <- compute(nn8, trainData[,-1])
trainpred8<- training.prediction8$net.result
rmsetrain8 <- sqrt(mean((trainpred8-trainData$Price)^2))
validation.prediction8 <- compute(nn8, validData[,-1])
validpred8<- validation.prediction8$net.result
rmsevalid8 <- sqrt(mean((validpred8-validData$Price)^2))
```

n=4
```{r}
nn9 <- neuralnet(Price~Age_08_04+KM+HP+cc, data=trainData, linear.output=FALSE,threshold=1, algorithm = 'rprop+',hidden=4)
training.prediction9 <- compute(nn9, trainData[,-1])
trainpred9<- training.prediction9$net.result
rmsetrain9 <- sqrt(mean((trainpred9-trainData$Price)^2))
validation.prediction9 <- compute(nn9, validData[,-1])
validpred9<- validation.prediction9$net.result
rmsevalid9 <- sqrt(mean((validpred9-validData$Price)^2))
```

n=8
```{r}
nn10 <- neuralnet(Price~Age_08_04+KM+HP+cc, data=trainData, linear.output=FALSE,threshold=1, algorithm = 'rprop+',hidden=8)
training.prediction10 <- compute(nn10, trainData[,-1])
trainpred10<- training.prediction10$net.result
rmsetrain10 <- sqrt(mean((trainpred10-trainData$Price)^2))
validation.prediction10 <- compute(nn10, validData[,-1])
validpred10<- validation.prediction10$net.result
rmsevalid10 <- sqrt(mean((validpred10-validData$Price)^2))
```

RMSE values for nn8, nn9, nn10 i.e. Neural networks with more than 1 hidden layer nodes
```{r}
rmsetrain1<-rbind(rmsetrain8, rmsetrain9, rmsetrain10)
rmsevalid1<-rbind(rmsevalid8, rmsevalid9, rmsevalid10)
rmsetrain1
rmsevalid1
```

THere is no definite pattern here, as RMS error for 2 hidden layer nodes network is the most, followed by 8 nodes and the 4 node netork has the least RMS error.

d) Neural network with the number of layers as 2 instead of 1
```{r}
nn11 <- neuralnet(Price~Age_08_04+KM+HP+cc, data=trainData,
linear.output=FALSE,threshold=1,algorithm='rprop+',hidden=c(1,2))
training.prediction11 <- compute(nn11, trainData[,-1])
trainpred11<- training.prediction11$net.result
rmsetrain2 <- sqrt(mean((trainpred11-trainData$Price)^2))
validation.prediction11 <- compute(nn11, validData[,-1])
validpred11<- validation.prediction11$net.result
rmsevalid2 <- sqrt(mean((validpred11-validData$Price)^2))
rmsetrain2
rmsevalid2

```


Neural network with number of layers as 1 in place of 2
```{r}
nn12 <- neuralnet(Price~Age_08_04+KM+HP+cc, data=trainData, linear.output=FALSE,threshold=1, algorithm='rprop+',hidden=c(2,1))
training.prediction12 <- compute(nn12, trainData[,-1])
trainpred12<- training.prediction12$net.result
rmsetrain3<- sqrt(mean((trainpred12-trainData$Price)^2))
validation.prediction12 <- compute(nn12, validData[,-1])
validpred12<- validation.prediction12$net.result
rmsevalid3 <- sqrt(mean((validpred12-validData$Price)^2))
rmsetrain3
rmsevalid3
```
With increase in number of hidden layers, RMS error decreases.

e)Introduction of learning rate (learning rate = 1):
```{r}
nn13 <- neuralnet(Price~Age_08_04+KM+HP+cc, data=trainData,
linear.output=FALSE,threshold=1,algorithm='rprop+',learningrate=1)
training.prediction13 <- compute(nn13, trainData[,-1])
trainpred13<- training.prediction13$net.result
rmsetrain4<- sqrt(mean((trainpred13-trainData$Price)^2))
validation.prediction13 <- compute(nn13, validData[,-1])
validpred13<- validation.prediction13$net.result
rmsevalid4<- sqrt(mean((validpred13-validData$Price)^2))
rmsetrain4
rmsevalid4
```

With learning rate = 1, RMS Error for training data is less than RMS error of test data.
