---
library(car)
library(ggplot2)
library(caret)
library(readxl)
#prepare the data

```{r}
dataset <- read_excel("ToyotaCorolla.xlsx",sheet="data")
#first step creat dummy varibale for the Fule Type and Color
#Fule_type
dataset$Fuel_Type = as.factor(dataset$Fuel_Type) 
dummy_FuelType = dummyVars("~Fuel_Type",data = dataset,sep = NULL) 
NewFule_type = data.frame(predict(dummy_FuelType,newdata = dataset))
#color
dataset$Color = as.factor(dataset$Color)
dummy_Color = dummyVars("~Color",data = dataset,sep = NULL) 
NewColor = data.frame(predict(dummy_Color,newdata = dataset))
#add the new dataset Fule_type and color to the dataset to prepare the data preprocessing
new_dataset = c(dataset, NewFule_type, NewColor) 
DataPreprocessing = as.data.frame(new_dataset)
```


Problem 1 
#A.1
```{r}
library(rpart)
library(rpart.plot)
set.seed(100)
RT <- rpart(Price ~ Age_08_04 + KM + Fuel_Type + HP + Automatic + Doors + Quarterly_Tax + 
                    Mfr_Guarantee + Guarantee_Period + Airco + Automatic_airco + CD_Player + Powered_Windows +
                    Sport_Model + Tow_Bar, method="anova", data = DataPreprocessing)
#for gettiing result 
printcp(RT)
#plot the result
plotcp(RT)
 
#find the best cp
pruned.ct = RT$cptable[which.min(RT$cptable[,"xerror"]),"CP"]
NEWRT = prune(RT, cp = pruned.ct)
prp(NEWRT, type = 3, extra = 1, split.font = 1, varlen = -10, fallen.leaves = T,main = "Regression Tree")  
```
#After we run the regression tree, we know that the Age, KM and HP are the three important car specifications for predicting the car's price.


#Split the data into trainging(50%),Validation(30%), and test(20%) 
```{r}
Train.data <- sample(row.names(DataPreprocessing), 0.5*dim(DataPreprocessing)[1])
TrainDP<- DataPreprocessing[Train.data,]

Valid.data <- sample(row.names(DataPreprocessing), 0.3*dim(DataPreprocessing)[1])
ValidDP<- DataPreprocessing[Valid.data,]

Test.data <- sample(row.names(DataPreprocessing), 0.2*dim(DataPreprocessing)[1])
TestDP<-DataPreprocessing[Test.data,]
```


```{r}
#for getting their RMS error 
PT = predict(NEWRT, TrainDP) 
PV = predict(NEWRT, ValidDP) 
PTE= predict(NEWRT, TestDP)

train_RMSE = sqrt(mean((PT-TrainDP$Price)^2)) 
valid_RMSE = sqrt(mean((PV-ValidDP$Price) ^2)) 
test_RMSE = sqrt(mean((PTE-TestDP$Price)^2)) 
#show the result
train_RMSE
valid_RMSE
test_RMSE
#plot the three boxplot 
par(mfrow=c(1,3))
boxplot(PT-TrainDP$Price)
boxplot(PV-ValidDP$Price)
boxplot(PTE-TestDP$Price)
```

#According to the result from two result we know that although the answer seems very similiar but the plot shows more accurate answer.



Classification Tree
#For the first step, create a new variable that categorizes price into 20 bins of equal counts.

```{r}
#creat the new varibale 
NEWVB<- cut(DataPreprocessing$Price, 20)
DataPreprocessing$Binned_price <- as.numeric(NEWVB)
```

```{r}
Train.data <- sample(row.names(DataPreprocessing), 0.5*dim(DataPreprocessing)[1])
TrainDP<- DataPreprocessing[Train.data,]

Valid.data <- sample(row.names(DataPreprocessing), 0.3*dim(DataPreprocessing)[1])
ValidDP<- DataPreprocessing[Valid.data,]

Test.data <- sample(row.names(DataPreprocessing), 0.2*dim(DataPreprocessing)[1])
TestDP<-DataPreprocessing[Test.data,]
```


```{r}
#use the binned price take place price

CL<- rpart(Binned_price ~ Age_08_04 + KM +
                Fuel_TypeDiesel + Fuel_TypeCNG + Fuel_TypePetrol+ HP + Automatic + Doors + Quarterly_Tax + 
                Mfr_Guarantee + Guarantee_Period + Airco + Automatic_airco + CD_Player + Powered_Windows + 
                Sport_Model + Tow_Bar,method="class",data=TestDP)


printcp(CL) 

plotcp(CL) 


prp(CL, type = 3, extra = 1, split.font = 1, varlen = -10, 
    fallen.leaves = T, main="Classification Tree")

```
Results of regression tree and classificiation tree is very similiar.The top predictor is almost the same while the classification tree has large size than regression tree.

#b.2
```{r}
NEWDATA= data.frame(Age_08_04 = 77, KM = 117000, Fuel_Type = "Petrol", Fuel_TypeCNG = 0, Fuel_TypeDiesel = 0,
                     Fuel_TypePetrol=1, HP = 110, Automatic = 0, Doors = 5, Quarterly_Tax = 100,
                     Mfr_Guarantee = 0, Guarantee_Period = 3, Airco = 1, Automatic_airco = 0,
                     CD_Player = 0, Powered_Windows = 0, Sport_Model = 0, Tow_Bar =1)

# RT prediction
RESULT_RT = predict(RT, NEWDATA) 
RESULT_RT

# CT prediction
RESULT_CL = predict(CL, NEWDATA) 
RESULT_CL
```
#The CL method has the less magnitude but has smaller size of data while the RT method has larger magnitude but has large size of data. All in all the results are very similiar and both contain the same top predictors. 
